### 2021-07-19 doc/thesis/chapters/system-design-process.tex
design for reuse

\includepicture [0.8] [0] {The SIMILAR process in a graphical representation.} {similar_process} {img/similar_process}

@@

The system launch actually runs the system in a defined environment, so that it can perform what it is intended and designed to do.
The defined environment can be the final, operational environment, or just a simulation which provides an output that is detailed enough for an evaluation.
In a product that involves hardware development, this step may include the installation of commercial-off-the-shelf products with a modified prototype software.
However, since the SIMILAR process is applicable for any kind of problem, this might also be a business process, where the launch step may be the roll-out of the subprocesses and tasks in the respective departments of a company.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design for Reuse}
%see pg. 51

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Problem Statement}

>>>>

\includepicture [0.7] [0] {The SIMILAR process in a graphical representation.} {similar_process} {img/similar_process}

@@

The system launch actually runs the system in a defined environment, so that it can perform what it is intended and designed to do.
The defined environment can be the final, operational environment, or just a simulation which provides an output that is detailed enough for an evaluation.
In a product that involves hardware development, this step may include the installation of commercial off-the-shelf products with a modified prototype software.
However, since the SIMILAR process is applicable for any kind of problem, this might also be a business process, where the launch step may be the roll-out of the subprocesses and tasks in the respective departments of a company.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design for Reuse}

A design principle that is often used is design for reuse.
It enables a faster and more efficient development of products, which leads to an overall decrease in development cost.
Additionally, the product is likely less error-prone, since the reused parts of the system are already tested at this point.
After all these positive arguments, there is a counter argument to it, though: designing a system with reuseable subsystems comes with cost.
Additional effort is required to design the subsystems in a way so that they can be reused in another project.
However, this additional effort may potentially already be paid off, when a single subsystem can be reused in a future product and thus, it is worth the effort.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Creation of a Problem Statement}
